Ohun: an R package for optimizing automatic acoustic signal detection

### 2022-05-12 manuscript/manuscript.Rmd
edit manuscript

@@

We recorded 30 individuals of Spix's disc-winged bats at Baru Biological Station, in south-western Costa Rica in January 2018. Bats were captured at their roosting sites (furled leaves of Zingeberaceae plants). Each individual bat was released in a large flight cage (9 x 4 x 3 m) for a 5 min period and their ultrasonic inquiry calls were recorded using a condenser microphone (CM16, Avisoft Bioacoustics, Glienike/
Nordbahn, Germany) through an Avisoft UltraSoundGate 116Hm connected to a laptop computer running Avisoft-Recorder software (sampling rate of 500 kHz, 16-bit amplitude resolution).

@@

Inquiry calls of Spix's disc-winged bats are stereotyped signals. Most variation is found between individuals although the basic structure of a short, downward broadband frequency modulation (FIG XXX) is always shared. Template-based detection is an useful approach when there is little structural differences in the target signals. Therefore we used the function

@@

We also used recordings from 18 zebra finch males. These recordings were obtained ....

>>>>

library(knitr)

```{r, echo = FALSE}

# knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())

opts_knit$set(root.dir = "..")

# opts_chunk$set(root.dir = "..")

@@

We recorded 30 individuals of Spix's disc-winged bats at Baru Biological Station, in south-western Costa Rica in January 2018. Bats were captured at their roosting sites (furled leaves of Zingeberaceae plants). Each individual bat was released in a large flight cage (9 x 4 x 3 m) for a 5 min period and their ultrasonic inquiry calls were recorded using a condenser microphone (CM16, Avisoft Bioacoustics, Glienike/Nordbahn, Germany) through an Avisoft UltraSoundGate 116Hm connected to a laptop computer running Avisoft-Recorder software, with a sampling rate of 500 kHz and a 16-bit amplitude resolution.

@@

Inquiry calls of Spix's disc-winged bats are stereotyped signals. Most variation is found between individuals although the basic structure of a short, downward broadband frequency modulation (Fig. bat-spectro) is always shared. Template-based detection is an useful approach when there is little structural differences in the target signals. Therefore we used the function.

```{r catalog, out.width = "100%", echo = FALSE, fig.align= "center"}

# knitr::include_graphics("./data/raw/thyroptera/Catalog_p1.jpeg")

knitr::include_graphics(normalizePath(file.path("./data/raw/thyroptera", "Catalog_p1.jpeg")))

list.files("./data/raw/thyroptera")
print(getwd())
```

Fig. bat-spectro.

@@

We used recordings from 18 zebra finch males. These recordings were obtained ....
